\documentclass[letter,draft]{article}
\usepackage[utf8]{inputenc}
\usepackage[margin=1in]{geometry}

\usepackage{biblatex}
\addbibresource{refs/refs.bib}

\title{CMSC457 Project Proposal}
\author{Christopher Berry, Gabriel Margolis, Rohith Venkatesh, Dan Zou}
\date{\today}

\begin{document}

\maketitle

\section{Motivation}
In deciding our motivation for the final project we opted to look at how
classical machine learning algorithms can be translated into the quantum field. 
More specifically the team is looking at either a Bayesian Network model or
Decision Tree/Random Forest approach. Although our topic is quite general right 
now the team hopes to narrow it down based upon research and Professor Wu’s
input. The ultimate goal is to find a niche/specific area the team can focus 
on with regards to these topics. This could possibly be theory based or more 
implementation based using code depending on where the research takes us. 

\section{Existing Literature}

There exists substantial existing literature describing machine learning
as well as specific machine learning models in the context of quantum
computing.

\section{Proposed Methodology}


\section{Timeline}

\begin{itemize}
  \item Course project proposals due by 02/12/21.
  \item Course project finalized by 02/19/21.
  \item Course project mid-term report due by 04/02/21.
  \item Course project slides due by 04/23/21.
  \item Course project presentation: online in the week of 05/03/21.
  \item Course project final report due by 05/17/21.
\end{itemize}

\printbibliography[heading=bibnumbered]
\end{document}
